%-------------------------
% Resume in Latex
% Author : Hnimtadd
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
% only for pdflatex
% \input{glyphtounicode}

% fontawesome
\usepackage{fontawesome5}

% fixed width
\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\DeclareRobustCommand{\ebseries}{\fontseries{eb}\selectfont}
\DeclareTextFontCommand{\texteb}{\ebseries}

% custom underilne
\usepackage{contour}
\usepackage[normalem]{ulem}
\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

% custom font: helvetica-style
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault}
%% Only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - serif
% \titleformat{\section}{
%   \vspace{2pt} \scshape \raggedright\large % header section
% }{}{0em}{}[\color{black} \titlerule \vspace{-5pt}]

% TODO EBSERIES
% sans serif sections
\titleformat {\section}{
  \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% only for pdflatex
% Ensure that generate pdf is machine readable/ATS parsable
% \pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
\item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}
\item
  \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ % top
    % row of resume entry
    \textit{#3} & {\color{dark-grey} \small #4}\\ % second row of resume entry
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small #2} \\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
\item
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    #1 & {\color{dark-grey}} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

% CHANGED default leftmargin  0.15 in
\newcommand{\resumeSubHeadingListStart}{
\begin{itemize}[leftmargin=0in, label={}]}
    \newcommand{\resumeSubHeadingListEnd}{
  \end{itemize}}
\newcommand{\resumeItemListStart}{
\begin{itemize}}
    \newcommand{\resumeItemListEnd}{
  \end{itemize}\vspace{0pt}}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge Nguyen Dinh Minh Dat} \\ \vspace{3pt}
  \small \faGithub \hspace{2pt} \texttt{github.com/hnimtadd}
  \hspace{1pt} $|$
  \hspace{1pt} \faLinkedin \hspace{2pt}
  \texttt{linkedin.com/in/hnimtadd} \hspace{1pt} $|$
  \hspace{1pt} \faGlobe \hspace{2pt}\texttt{www.info.craftznake.space}
  \\ \vspace{-5pt}
\end{center}

%-----------EXPERIENCE-----------
\section{EXPERIENCE}
\resumeSubHeadingListStart

\resumeSubheading
{Grab}{May 2024 -- Present}
{Software Engineer}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\resumeItem{Spearheaded the engineering of a production-ready API Gateway on Envoy Proxy, serving as the primary entry point for major public-facing traffic; \textbf{implemented} core security features including authentication, circuit breakers, and outlier detection; log analysis pipeline for traffic observability.}
\resumeItem{Core member of a massive migration for \textbf{1,000+ microservices (300k+ QPS)} from legacy systems to a unified gateway; developed feature parity for \textbf{20+ capabilities} supporting \textbf{3 gateway migrations} into a single standardized solution.}
\resumeItem{Optimized end-to-end client latency by \textbf{80\%} for high-payload requests by implementing advanced compression algorithms at the gateway level.}
\resumeItem{Architected a Multi-Tenant Self-Serve Console with RBAC, enabling service owners to autonomously manage service configurations, authentication, and rate limiting.}
\resumeItem{Engineered a Dynamic Configuration CI/CD Pipeline with automated smoke testing and configuration validation, ensuring safe deployments without service disruption; reduced global rollout time from \textbf{60 minutes to 5 minutes}.}
\resumeItem{Architected and maintained a full-feature Disaster Recovery (DR) platform, successfully executing \textbf{production traffic flips} to ensure business continuity during primary data center outages.}
\resumeItem{Built an AI-driven Multi-Agent LLM Support Bot using a supervisor architecture to automate technical troubleshooting, significantly reducing manual query resolution time for internal developers.}
\resumeItemListEnd

% \resumeSubheading
% {Walless.io}{May 2024 -- Aug. 2024}
% {Software Engineer}{Ho Chi Minh City, Vietnam}
% \resumeItemListStart
% \resumeItem{Developed personalized Web3 wallet application with
% streamlined user experience for cryptocurrency management}
% \resumeItem{Architected and implemented comprehensive Profit \& Loss
% tracking feature for real-time portfolio analytics}
% \resumeItemListEnd

\resumeSubheading
{Peakee.io}{Aug. 2023 -- May 2024}
{Software Engineer}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\resumeItem{Architected a context-aware language learning platform that unified data from \textbf{multiple touchpoints} --- mobile app, web browser, and Chromium extension --- to build comprehensive learner profiles.}
\resumeItem{Designed \textbf{intelligent data ingestion pipeline} capturing user interactions across platforms: translation clicks, mobile practice sessions, and AI agent conversations, enabling \textbf{personalized, tailored content recommendations} based on real usage patterns.}
\resumeItem{Developed cross-platform client (mobile, web, browser extension) from unified codebase, reducing \textbf{development overhead by 60\%} while maintaining consistent user experience across all surfaces.}
\resumeItemListEnd

\resumeSubheading
{VinAI}{June 2023 -- Oct. 2023}
{Software Engineer Intern}{Ho Chi Minh City, Vietnam}
\resumeItemListStart
\resumeItem{Developed a \textbf{video streaming platform} with intelligent search using Elasticsearch and adaptive bitrate encoding server}
\resumeItem{Built a full-text search engine for video captured events using Elasticsearch and MongoDB, enabling \textbf{fast and accurate keyword-based video retrieval} from over millions of records.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{PROJECTS}
\resumeSubHeadingListStart
\resumeProjectHeading
{\small RUN $|$ \emph{Go, Wazero, Proto Actor, Docker} $|$
\href{https://github.com/hnimtadd/run}{\myuline{github.com/hnimtadd/run}}}{Feb.
2024 -- June 2025}
\vspace{-8pt}
\resumeItem{Edge computing platform for \textbf{WebAssembly binaries}, supporting service deployment and lifecycle management}

\resumeProjectHeading
{\small SPACED $|$ \emph{HTML, CSS, JavaScript, Go, WASM, Tailwind} $|$
\href{https://github.com/hnimtadd/spaced}{\myuline{github.com/hnimtadd/spaced}}}{July
2025 -- Aug. 2025}
\vspace{-8pt}
\resumeItem{Serverless flashcard app with \textbf{FSRS} algorithm; leveraged WASM for near-native browser performance}

\resumeProjectHeading
{\small TERMIO $|$ \emph{Go, Nix} $|$
\href{https://github.com/hnimtadd/termio}{\myuline{github.com/hnimtadd/termio}}}{Apr.
2025 -- Dec. 2025}
\vspace{-8pt}
\resumeItem{Terminal emulator engine with \textbf{VT100/Xterm compatibility}, escape sequence processing, and UTF-8 support}
\vspace{-2pt}
\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{TECHNICAL SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
  \small{
  \item{
      \textbf{Go, Python, Rust, AWS, Docker, Terraform, Envoy Proxy, WebAssembly, MongoDB, PostgreSQL, Elasticsearch, Git, CI/CD}
  }}
\end{itemize}

%-----------EDUCATION & AWARDS-----------
\section{EDUCATION \& AWARDS}
\resumeSubHeadingListStart
\resumeSubheading
{Ho Chi Minh University of Technology}{Aug. 2020 -- May 2024}
{Bachelor of Computer Science, GPA: 8.3/10.0}{Ho Chi Minh City, Vietnam}
\resumeSubSubheading
{TOEIC: 870}{}
\resumeSubheading
{\href{https://sites.google.com/grabtaxi.com/tech-infra-appreciation-board/appreciation-board/july}{\myuline{First Grab Rising Star Award}}}{July 2025}
{Issued by Grab}{Recognized for exceptional performance and impact}
\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
